The noise-marginalized optimal statistic: A robust hybrid frequentist-Bayesian statistic for the stochastic gravitational-wave background in pulsar timing arrays

### 2018-05-30 manuscript/manuscript.tex
added grant numbers

\acknowledgments
We thank Joe Lazio, Andrea Lommen, Joe Romano, Xavier Siemens, 
and Jolien Creighton for useful discussions. 
This work was supported by NSF Physics Frontier Center Grant 1430284. 
%SRT was partially supported by appointment to the NASA Postdoctoral Program 
%at the Jet Propulsion Laboratory, which is administered by Oak Ridge Associated Universities 
%and the Universities Space Research Association through a contract with NASA. 
JAE was partially supported by NASA through Einstein Fellowship Grant PF4-150120. 
We are grateful for computational resources provided by the Leonard E Parker
Center for Gravitation, Cosmology and Astrophysics at the University of
Wisconsin-Milwaukee supported by NSF Grant 0923409.

>>>>

\acknowledgments
We thank Joe Lazio, Andrea Lommen, Joe Romano, Xavier Siemens, 
and Jolien Creighton for useful discussions. 
This work was supported by NSF Physics Frontier Center Grant 1430284. 
%SRT was partially supported by appointment to the NASA Postdoctoral Program 
%at the Jet Propulsion Laboratory, which is administered by Oak Ridge Associated Universities 
%and the Universities Space Research Association through a contract with NASA. 
JAE was partially supported by NASA through Einstein Fellowship Grant PF4-150120. 
We are grateful for computational resources provided by the Leonard E Parker
Center for Gravitation, Cosmology and Astrophysics at the University of
Wisconsin-Milwaukee, which is supported by NSF Grants 0923409 and 1626190.
